A large-scale analysis of racial disparities in police stops across the United

### 2019-12-05 lib/paper_results.Rmd
progress

We have collected and released a dataset of 
`r comma_num(pfs$counts$collected$n_stops)` traffic stops carried out by 
`r pfs$counts$collected$n_states` (`r pfs$counts$collected$n_stops_states`)
state patrol agencies and
`r pfs$counts$collected$n_cities` (`r pfs$counts$collected$n_stops_cities`)
municipal police departments.

We analyzed a unique dataset detailing 
`r comma_num(pfs$counts$analyzed$n_stops)` traffic stops carried out by 
`r pfs$counts$analyzed$n_states` (`r pfs$counts$analyzed$n_stops_states`)
state patrol agencies and
`r pfs$counts$analyzed$n_cities` (`r pfs$counts$analyzed$n_stops_cities`)
municipal police departments.

@@

```{r stop_rates}
pfs$rates$stop %>%
  mutate(agency = if_else(city == "Statewide", "state patrol", "municipal pd")) %>% 
  group_by(agency, subject_race) %>%
  summarize(average_annual_stop_rate = mean(annual_stop_rate)) %>%
  kable()
```

Number of state patrols with data for search analysis: 
`r pfs$rates$search %>% filter(city == "Statewide") %>% select(state) %>% n_distinct`
Number of city departments with data for search analysis: 
`r pfs$rates$search %>% filter(city != "Statewide") %>% select(state, city) %>% n_distinct`

```{r search_rates}
pfs$rates$search %>% 
  mutate(agency = if_else(city == "Statewide", "state patrol", "municipal pd")) %>% 
  group_by(agency, subject_race) %>%
  summarize(average_search_rate = mean(search_rate)) %>%
  kable()
```

@@

```{r veil_of_darkness-plot-630, fig.height=6, fig.width=9}
vod$full$plots$states$TX$`6:30pm`
```

```{r veil_of_darkness-plot-645, fig.height=6, fig.width=9}
vod$full$plots$states$TX$`6:45pm`
```

```{r veil_of_darkness-plot-700, fig.height=6, fig.width=9}
vod$full$plots$states$TX$`7:00pm`
```

```{r veil_of_darkness-plot-715, fig.height=6, fig.width=9}
vod$full$plots$states$TX$`7:15pm`
```

```{r veil_of_darkness-plot-730, fig.height=6, fig.width=9}
vod$full$plots$states$TX$`7:30pm`
```

```{r veil_of_darkness-plot-745, fig.height=6, fig.width=9}
vod$full$plots$states$TX$`7:45pm`
```

@@

```{r veil_of_darkness-main_mod}
vod$dst %>% 
  filter(spline_degree == 6, agency_control, !interact_time_loc) %>% 
  kable()
```

@@

```{r veil_of_darkness-appendix_mods}
bind_rows(
  vod$dst %>%
    mutate(model = "DST"),
  vod$full$coefficients %>%
    mutate(model = "Full year")
) %>%
  select(model, agency, is_dark, std_error, everything()) %>%
  kable()
```

@@

State patrol agencies analyzed: 
`r disp$state$outcome$results$hit_rates$geography %>% unique()`
Number of state patrol searches: 
`r disp$state$outcome$results$hit_rates$n_search_conducted %>% sum()`
Municipal departments analyzed:
`r disp$city$outcome$results$hit_rates$geography %>% unique()`
Number of municipal pd searches: 
`r disp$city$outcome$results$hit_rates$n_search_conducted %>% sum()`

@@

City and State outcomes:
```{r disparity-hit_rates-tables}
kable(disp$city$outcome$results$aggregate_hit_rates)
kable(disp$state$outcome$results$aggregate_hit_rates)
```

>>>>

We have collected and released a dataset of 
`r comma_num(pfs$counts$collected$n_stops)` traffic stops carried out by 
`r pfs$counts$collected$n_states` (`r comma_num(pfs$counts$collected$n_stops_states)`)
state patrol agencies and
`r pfs$counts$collected$n_cities` (`r comma_num(pfs$counts$collected$n_stops_cities)`)
municipal police departments.

We analyzed a unique dataset detailing 
`r comma_num(pfs$counts$analyzed$n_stops)` traffic stops carried out by 
`r pfs$counts$analyzed$n_states` (`r comma_num(pfs$counts$analyzed$n_stops_states)`)
state patrol agencies and
`r pfs$counts$analyzed$n_cities` (`r comma_num(pfs$counts$analyzed$n_stops_cities)`)
municipal police departments.

@@

```{r stop_rates}
pfs$rates$stop %>%
  mutate(agency = if_else(city == "Statewide", "state patrol", "municipal pd")) %>% 
  group_by(agency, subject_race) %>%
  summarize(
    average_annual_stop_rate = mean(annual_stop_rate)
  ) %>%
  kable()
```

Number of state patrols with data for search analysis: 
`r pfs$rates$search %>% filter(city == "Statewide") %>% select(state) %>% n_distinct`

Number of city departments with data for search analysis: 
`r pfs$rates$search %>% filter(city != "Statewide") %>% select(state, city) %>% n_distinct`

```{r search_rates}
pfs$rates$search %>% 
  mutate(agency = if_else(city == "Statewide", "state patrol", "municipal pd")) %>% 
  group_by(agency, subject_race) %>%
  summarize(
    average_search_rate = mean(search_rate),
    std_error = sqrt(
      average_search_rate * (1 - average_search_rate) / mean(n)
    ),
    CI_lower = average_search_rate - 1.96 * std_error,
    CI_upper = average_search_rate + 1.96 * std_error
  ) %>%
  select(-std_error) %>% 
  kable()
```

@@

Number of points in 7:00-7:15pm panel:
`r vod$full$plots$states$TX$`7:00pm`$data$n %>% sum() %>% comma_num()`

Number of points in 7:15-7:30pm panel:
`r vod$full$plots$states$TX$`7:15pm`$data$n %>% sum() %>% comma_num()`

Number of points in 7:30-7:45pm panel:
`r vod$full$plots$states$TX$`7:30pm`$data$n %>% sum() %>% comma_num()`

@@

```{r veil_of_darkness-main_mod}
vod$dst %>% 
  select(-data, -base_controls) %>% 
  filter(spline_degree == 6, agency_control, !interact_time_loc) %>% 
  kable()
```

@@

```{r veil_of_darkness-appendix_mods}
bind_rows(
  vod$dst %>%
    select(-data, -base_controls) %>% 
    mutate(model = "DST"),
  vod$full$coefficients %>%
    select(-data, -base_controls) %>% 
    mutate(model = "Full year")
) %>%
  arrange(model, agency_control, interact_time_loc, spline_degree) %>% 
  select(model, agency, is_dark, std_error, p_value, everything()) %>%
  kable()
```

@@

State patrol agencies analyzed: 
`r disp$state$outcome$results$hit_rates$geography %>% unique()`

Total number of state patrol searches: 
`r disp$state$outcome$results$hit_rates$n_search_conducted %>% sum() %>% comma_num()`

Municipal departments analyzed:
`r disp$city$outcome$results$hit_rates$geography %>% unique()`

Total number of municipal pd searches: 
`r disp$city$outcome$results$hit_rates$n_search_conducted %>% sum() %>% comma_num()`

@@

City and State outcomes:
```{r disparity-hit_rates-tables}
rbind(
  disp$city$outcome$results$aggregate_hit_rates %>% 
    mutate(
      geography = "cities",
      std_error = sqrt(hit_rate * (1 - hit_rate) / n),
      lower_CI = hit_rate - 1.96 * std_error,
      upper_CI = hit_rate + 1.96 * std_error
    ),
  disp$state$outcome$results$aggregate_hit_rates %>% 
    mutate(
      geography = "states",
      std_error = sqrt(hit_rate * (1 - hit_rate) / n),
      lower_CI = hit_rate - 1.96 * std_error,
      upper_CI = hit_rate + 1.96 * std_error
    )
) %>% 
  select(-std_error) %>% 
  select(geography, everything())
  kable()
```
